Pottery decor as networks on the Middle Niger

### 2024-03-04 analysis/paper/paper.Rmd
updated data

decors <- read_csv2(here::here("analysis/data/raw_data/decors_late.csv")) |>
  select(-1)

# import information on sites
sites <- read_csv2(here::here("analysis/data/raw_data/sites_all.csv"))

@@

```{r community detection, hide = 'results', echo=FALSE}
# use louvain clustering method to assign clusters to nodes
decor_graph <- decor_graph |>
  activate(nodes) |>
  mutate(louvain = as.character(group_louvain()))

@@

```{r import-new-data}
library(readr)
decorsearly <- 
  read_csv2(here::here("analysis/data/raw_data/decors_early.csv")) |>
  select(-1)

>>>>

decors <- read_csv2(here::here("analysis/data/raw_data/decors12.csv")) |>
  select(-1) |> 
  rename(sites = Site) |> 
  select(-slip, -unidentified_roulette, -"twisted_cord_roulette?")

# import information on sites
sites <- read_csv2(here::here("analysis/data/raw_data/sites_all3.csv"))

@@

```{r community detection, hide = 'results', echo=FALSE}
# use louvain clustering method to assign clusters to nodes
decor_graph <- decor_graph |>
  activate(nodes) |>
  mutate(louvain = as.character(group_optimal()))

@@

```{r import-new-data}
library(readr)
decorsearly <- 
  read_csv2(here::here("analysis/data/raw_data/decors9.csv")) |>
  select(-1)
